testing_summary

### 2025-03-19 data-raw/testing_summary.Rmd

+ fold_errors.pk()  
+ residuals.pk()  
+ rsq.pk()  
+ rmse.pk()

@@

```{r}
my_residuals <- residuals(my_pk)
my_fes <- fold_errors(my_pk)
my_rmse <- rmse(my_pk)
my_rmsle <- rmse(my_pk, use_scale_conc = list(dose_norm = FALSE,
                                              log10_trans = TRUE))

>>>>

+ fold_error.pk()  
+ residuals.pk()  
+ rsq.pk()  
+ rmse.pk()

@@

```{r}
my_residuals <- residuals(my_pk)
my_fes <- fold_error(my_pk)
my_rmse <- rmse(my_pk)
my_rmsle <- rmse(my_pk, use_scale_conc = list(dose_norm = FALSE,
                                              log10_trans = TRUE))
